Results

### 2018-04-25 3-simus.Rmd
add biglasso to simulations

@@

>>>>

### Logistic regression with biglasso

```{r}
logit.biglasso <- function(G3, pheno.all, covar.all, ind.train, ind.test) {

    biglasso <- biglasso(G3, pheno.all, ind.train, ncores = nb_cores(),
                         penalty = "enet", family = "binomial", alpha = 0.5)

    preds <- 1 / (1 + exp(-predict(biglasso, G3, ind.test)))
  })[3]

  aucs <- apply(preds, 2, bigstatsr::AUC, target = pheno.all[ind.test])
  ind.max <- which.max(aucs)

  tibble(
    method   = "biglasso", 
    eval     = list(cbind(preds[, ind.max], pheno.all[ind.test])),
    timing   = timing,
    nb.preds = sum(biglasso$beta[, ind.max] != 0)
  )
}
```

@@

### Scenario n°1 (comparison with biglasso)

```{r}
library(biglasso)
library(Matrix)
```

```{r, eval=FALSE}
G3 <- big.matrix(nrow(G), ncol(G) + ncol(covar.all),
                 backingfile = "G-PC", 
                 backingpath = "backingfiles")
big_apply(G, function(X, ind) {
  G3[, ind] <- X[, ind]
  NULL
}, a.combine = 'c')
G3[, ncol(G) + cols_along(covar.all)] <- covar.all
```

```{r}
G3 <- attach.big.matrix("backingfiles/G-PC.desc")
```

```{r}
params.grid7 <- expand.grid(
  n.train = 6000,
  par.causal = list(c(30, "all"), c(300, "all"), c(3000, "all"), c(30, "HLA")), 
  par.dist   = c("gaussian", "laplace"), 
  par.h2     = c(0.8), 
  par.model  = c("simple"),
  num.simu   = 1:100,
  stringsAsFactors = FALSE
) 
```

```{r, eval=TRUE}
if (!dir.exists("results7")) dir.create("results7")

for (i in rows_along(params.grid7)) {

  res.file <- paste0("results7/simu_", i, ".rds")
  if (file.exists(res.file)) next

  params <- params.grid7[i, ]
  par.causal <- params[["par.causal"]][[1]]

  # Get results from all methods
  res <- bind_rows(
    logit.CMSA(G, pheno.all, covar.all, ind.train, ind.test, "logit-simple"),
    logit.biglasso(G3, pheno.all, covar.all, ind.train, ind.test)
  )
  params[["res"]] <- list(res)
  saveRDS(unnest(params, res, .drop = FALSE), file = res.file)
}
```

### 2018-04-25 4-results-simus.Rmd
save figures
add biglasso to simulations

---
title: "Results"
author: "Florian Privé"
date: "November 17, 2017"
output: 
  html_document:
    code_folding: hide
params:
  ggsave: false
---

@@

methods.color <- setNames(scales::hue_pal()(6), 
                          c("logit-simple", "PRS-max", "PRS-stringent",
                            "T-Trees", "logit-triple", "PRS-all")) 
```

@@

>>>>

---
title: "Results"
author: "Florian Privé"
date: "November 17, 2017"
output: 
  html_document:
    code_folding: hide
---

@@

methods.color <- setNames(c(scales::hue_pal()(6), "black"), 
                          c("logit-simple", "PRS-max", "PRS-stringent",
                            "T-Trees", "logit-triple", "PRS-all", "biglasso")) 
```

@@

### Comparison with biglasso

```{r}
results7 <- list.files("results7", full.names = TRUE) %>%
  map_dfr(~readRDS(.x)) %>%
  format_results()
```

```{r}
compare_logit(results7, "biglasso")

ggsave("figures/supp-biglasso.pdf", scale = 1/100, width = 1600, height = 1000)
```
